Adaptive Hierarchical Sliding Mode Control with Input Saturation for Attitude Regulation of Multi-satellite Tethered System

### 2016-07-11 manuscript.tex
20160711

Figure~\ref{Figure:modelsinglebody} shows an individual participating satellite which rotates about the center of the array frame. \begin{color}{red}Body coordinate system $x$-$y$ requires that y axis points to the direction of the increase of the array rotation angle, and meanwhile $x$-axis is along the tether\end{color}. Assume that the tether is massless and inextensible so that the vibration dynamics can be regardless. The Kevlar physical property makes the tether strong and thin enough, i.e., SPECS owns the tether consisting of four tethers lines, and the total mass is approximate to 30 \textit{kg} for 1-km-long ribbon tether\cite{chung2007nonlinear1}. \begin{color}{red}The three-satellite inline tethered frame is assumed to rotate at a specific angular rate so that the tether keeps taut.\end{color} Since the tether speed can be easily controlled by programmed tether motor and doesn't disturb any other system states, it's assumed that the tether length speed $\dot l$ is naught. Finally, assume the three-satellite inline tethered frame is manoeuvred to orbit in the second Lagrangian point of the earth-sun system referring to the SPECS project, and hence the gravity term is approximate to zero~\cite{lorenzini2006far}.\par

@@

The mathematical form of $d_i(X,t)$ is trigonometric term, and the detail of $d_i(X,t)$ will be given in Section~\ref{sec:sm}. Assumption~\ref{as:2} is reasonable since there exists the boundary of the perturbation mentioned above. In addition, it is obvious that the terms in the individual satellite system~(\ref{eq:3bodyreduce}) consist of the trigonometric and constant terms, and hence the extremes of $\vert c_1x_2+f_1(X,t)\vert$ and $\vert c_2x_4+f_2(X,t)\vert$ can be obtained by using mathematical calculation. In the regulation, the attitude angle is limited in a practical meaningful range $\vert x_3\vert<\pi/2$~\cite{chung2008propellant2}.

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$ with $\vert x_3\vert<\pi/2$.

@@

    This can guarantee the non-singularity of Eq.~(\ref{eq:u}), when $x_3$ is varying in a small region with $\vert x_3\vert<\pi/2$.

@@

Some essential results are given in advance so that the adaptive control design for the system~(\ref{eq:2model}) can be illustrated explicitly. The spatial perturbation term, $d_i(X,t)$, owns the characteristics of trigonometric function, and those bound value can be determined easily. More notably, the terms in the attitude dynamics of the two-satellite system~(\ref{eq:2body}) are a group of constant and trigonometrical terms, and furthermore, their operations are additive and multiplicative. Hence the boundary exists and can be calculated. In the regulation, the attitude angle is limited in a practical meaningful range $\vert \phi_i\vert<\pi/2$~\cite{chung2008propellant2}. Therefore, some symbols are introduced to express the mentioned relationship, and they will take part in the design of the adaptive control in the following form:\label{rem:2}

@@

    where $\vert\phi_1\vert<\pi/2$ and $\vert\phi_2\vert<\pi/2$.

>>>>

Figure~\ref{Figure:modelsinglebody} shows an individual participating satellite which rotates about the center of the array frame. \begin{color}{red}Body coordinate system $x$-$y$ requires that y axis points to the direction of the increase of the array rotation angle, and meanwhile $x$-axis is along the tether\end{color}. Assume that the tether is massless and inextensible so that the vibration dynamics can be regardless. The Kevlar physical property makes the tether strong and thin enough, i.e., SPECS owns the tether consisting of four tethers lines, and the total mass is approximate to 30 \textit{kg} for 1-km-long ribbon tether\cite{chung2007nonlinear1}. \begin{color}{red}The three-satellite inline tethered frame is assumed to rotate at a specific angular rate so that the tether keeps taut. In reality, the satellite will hit the tether when attitude angle $\phi_i$ crosses $\pi/2$ rad, and due to the rotation dynamics of the array and the small initial condition of $\phi_i$, we can assume that $\vert \phi\vert\le \pi/2$~\cite{chung2007nonlinear1}.\end{color}  Since the tether speed can be easily controlled by programmed tether motor and doesn't disturb any other system states, it's assumed that the tether length speed $\dot l$ is naught. Finally, assume the three-satellite inline tethered frame is manoeuvred to orbit in the second Lagrangian point of the earth-sun system referring to the SPECS project, and hence the gravity term is approximate to zero~\cite{lorenzini2006far}.\par

@@

The mathematical form of $d_i(X,t)$ is trigonometric term, and the detail of $d_i(X,t)$ will be given in Section~\ref{sec:sm}. Assumption~\ref{as:2} is reasonable since there exists the boundary of the perturbation mentioned above. In addition, it is obvious that the terms in the individual satellite system~(\ref{eq:3bodyreduce}) consist of the trigonometric and constant terms, and hence the extremes of $\vert c_1x_2+f_1(X,t)\vert$ and $\vert c_2x_4+f_2(X,t)\vert$ can be obtained by using mathematical calculation. In the regulation, the attitude angle is limited in a practical meaningful range $\vert x_3\vert\le\pi/2$~\cite{chung2008propellant2}.

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$ with $\vert x_3\vert\le\pi/2$.

@@

    This can guarantee the non-singularity of Eq.~(\ref{eq:u}), when $x_3$ is varying in a small region with $\vert x_3\vert\le\pi/2$.

@@

Some essential results are given in advance so that the adaptive control design for the system~(\ref{eq:2model}) can be illustrated explicitly. The spatial perturbation term, $d_i(X,t)$, owns the characteristics of trigonometric function, and those bound value can be determined easily. More notably, the terms in the attitude dynamics of the two-satellite system~(\ref{eq:2body}) are a group of constant and trigonometrical terms, and furthermore, their operations are additive and multiplicative. Hence the boundary exists and can be calculated. In the regulation, the attitude angle is limited in a practical meaningful range $\vert \phi_i\vert\le\pi/2$~\cite{chung2008propellant2}. Therefore, some symbols are introduced to express the mentioned relationship, and they will take part in the design of the adaptive control in the following form:\label{rem:2}

@@

    where $\vert\phi_1\vert\le\pi/2$ and $\vert\phi_2\vert\le\pi/2$.
